Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-01 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Frame work

\section{HC  IEC Framework}
% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
The general goal of this research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
The framework is a reusable architectural design together with an implementation \cite{campbell1991choices}, 
providing generalized components to developers of IEC systems. In the description we deliberately use the more general term Human instead of User, because humans are not always playing the role of users in software engineering sense, they could just be interacting naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. The framework includes components that can be refined to increase
participation and also to minimize the amount of evaluations needed for the evolutionary process in a given IEC application.

  \subsection{Real World}
  \subsection{Data Model}
  \subsection{Evolutionary Algorithm}

>>>>

\section{HC  IEC Framework}
% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
The general goal of this research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
The framework is a reusable architectural design together with an implementation \cite{campbell1991choices}, 
providing generalized components to developers of IEC systems. In the description we deliberately use the more general 
term Human instead of User, because humans are not always playing the role of users in software engineering sense, they
could just be interacting naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. The framework includes components that can be refined to increase
participation and also to minimize the amount of evaluations needed for the evolutionary process in a given IEC application. Software frameworks often have a vison or a way of thinking \cite{carneiro2010introducing} guiding their
design. Before entering to details the main design decisions of the framework are explained next:

\begin{itemize}
\item {\bf Users are human} 
  The framework follows the approach of human centered computing \cite{sebe2010human},
  in which the context, environment, interfaces, preferences, accessibility, human relations, cognitive
  limitations, culture, creativity and other human aspects are an integral part of the system.
  Humans are the computing resorces of the system, having unique characteristics as those identified by 
  Sun \& Dance \cite{Sun2013}  ``(1) humans can solve computer hard problems; (2) humans are very good at exception handling, (3) humans have creativity, (4) humans have cognitive load limitation, (5) humans are vulnerable to 
  psychological manipulation, (6) humans are prone to errors, especially for reflective tasks.''

\item {\bf Users are volunteers} Users donate their computing resources, so they are unaccountable, 
  some times they try to game the system. Providers must actively promote and design the interactive
  system to engage volunteers \cite{oh2015clicking}.

\item {\bf Users are not alone}
  Relationship between users in an interactive evolutionary algorithm can be modeled
  as a social network, with well established semantics, algorithms and metrics \cite{ahuja1993network}.
  A graph model could enable researchers to find other ways of identifying leaders of 
  opinion or measuring the similarity between user's preferences. 
  These measures can then be used by recommender algorithms selecting 
  phenotypes according users' preferences.

\item {\bf Context of use matters}
  \textit{Context} In computer science Fischer \cite{fischer2012context}
  defines context as \textit{``the interaction between humans and
  computers in socio-technical systems that takes place in a certain
  context referring to the physical and social situation in which
  computational devices and environments are embedded"}. 
  Fischer also identifies the important aspects to consider when the context is used: how it is
  the contextual data obtained, how the context is represented and what
  goals and purposes the context has when is used in a particular
  application.   An IEC system will  be used within a certain range of technical, physical and social or
  organizational environments \cite{maguire2001context} that may affect its use.
  The concept has been formally defined
  by ISO standard 9241-11 \cite{international1998iso} as \textit{``users,
  tasks and equipment (hardware, software and materials), and the
  physical and social environments in which a product is used"}.

\item {\bf Interaction is a stream of actions}
  Real time processing of users' actions could be needed for certain applications when data is 
  captured by sensors, or directly captured as user input.
  Graph based models are currently used in social networks to keep track  
  of user interactions with media objects, places, and other users. Users of 
  social networks (for instance the Facebook Graph) are accustomed to express these 
  complex relationships in sentences such as: ``John and Ann eating breakfast at Tony's''. 
  Other example is the W3C Activity Streams 2.0 specification used for representing activities 
  common in social web applications \cite{json:streams}. An important component of the 
  framework is the stream of user-activities.
\end{itemize}

The human centered framework consists of three high level components depicted
in figure \ref{fig:uc_framework}:

\begin{itemize}
  \item {\bf Interactive Evolutionary Computational system} 
  This is the real world system that we are going to represent in the model, 
  it consist of human users and their interactions with one or more phenotypes
  from
  the population. There are many ways in which humans could interact 
  with phenotypes, this could be through a mobile device, a user interface 
  or by interacting with real world objects generated as part of the algorithm 
  \cite{de2014artists,de2013unplugging}. 
  There is also the possibility that fitness or even part of the search 
  to be done by devices lent by the human \cite{DBLP:conf/gecco/MereloCGCRV16}.
  The information gathered through the interaction is the primary concern
  as it will guide the search.

  \item {\bf IEC Data Model}
  A data model is used to describe the IEC system prior to a physical 
  implementation.  Depending on the domain several techniques can be used.
  Parts of the system could be better described by an Entity relationship 
  modeling to be used in a relational database or a class digram for a 
  key-value store.

  A graph is proposed for modeling the social network of users 
  and their interaction with the population. When implemented a graph database 
  will be the back-end of the system. This  backend will then be
  used by the EA and the user interface, in a Model-View-Controller architecture.

  \item {\bf Evolutionary Algorithm} 
  The EA algorithm queries the graph model, and then updates those nodes that 
  are part of the population. The EA could also be done with the help of
  humans, for instance in the XY project \cite{de2013unplugging} artists physically created
  the new population.  
\end{itemize}

  \subsection{Evolutionary Algorithm}
